### 2021-01-13 manuscript.tex
changed rendering flow fig to represent multiple files
create parse_flow fig; made other formatting updates across all figs

@@

Throughout the course of the project we utilized a private github code repository for hosting and change tracking. This work has since been published on a public repository and assigned a DOI number through Zenodo~\cite{Tastad}. Furthering the spirit of project integrity, we expanded on the nature of the documentation for the user and, more prominently, the application owner. Specifically, documentation that was previously written in a Microsoft Word file was now recreated in markdown, and a notable tone and detail shift was made in serving the information transportability between administrators.

>>>>

\begin{figure}[H]
    \centering
    \includegraphics[width=\textwidth]{fig/parse_flow.png}
    \caption{Project directory file tree comparison}\label{fig:parseFlow}
\end{figure}

@@

Throughout the course of the project we utilized a private github code repository for hosting and change tracking. This work has since been published on a public repository and assigned a DOI number through \href{https://zenodo.org/record/4422027}{Zenodo}. Furthering the spirit of project integrity, we expanded on the nature of the documentation for the user and, more prominently, the application owner. Specifically, documentation that was previously written in a Microsoft Word file was now recreated in markdown, and a notable tone and detail shift was made in serving the information transportability between administrators.
